Automated Example Oriented REST API Documenation

### 2017-07-23 root.tex
abstract v1

%
%                 Substitute  List of Examiners
%
\begin{signing}{Department of Computer Science}
\signline
Dr. Frank Maurer \\
Supervisor\\
Department of Computer Science \\
University of Calgary \\
Canada\\
\signline
Dr. Mea Wang\\
Supervisory Committee Member\\
Department of Computer Science \\
University of Calgary \\
Canada\\
\signline
Dr. Craig Anslow\\
Supervisory Committee Member\\
School of Eng. and Computer Science \\
Victoria University of Wellington\\
New Zealand\\
\end{signing}
%
\newpage
\phantomsection
\altchapter{\bf{Abstract}}
\newpage
\phantomsection
\altchapter{\bf{Acknowledgements}}

>>>>

%
%                 Substitute  List of Examiners
%
\begin{signing}{Department of Computer Science}
\signline
Dr. Frank Maurer \\
Supervisor\\
Department of Computer Science \\
University of Calgary \\
Canada\\
\signline
Dr. Mea Wang\\
Supervisory Committee Member\\
Department of Computer Science \\
University of Calgary \\
Canada\\
\signline
Dr. Craig Anslow\\
Supervisory Committee Member\\
School of Eng. and Computer Science \\
Victoria University of Wellington\\
New Zealand\\
\end{signing}
%
\newpage
\phantomsection
\altchapter{\bf{Abstract}}
API documentation presents both a problem and an opportunity for API usability. Most developers learn to use an API based on its documentation and at the same time face obstacles using the APIs due to lack of necessary information in the documentation \cite{Robillard_what_makes}. REST APIs provide interconnectivity between applications over HTTP. Documentation of a REST API is a key information source for software developers that use these types of API. As a REST API evolves, the documentation needs to be maintained alongside. This implies that REST API developers also need to efficiently generate and maintain the documentation of their APIs with the qualities that make the API usable. This introduces the problem of interest in this research: how to document REST APIs?

This is a problem because there is a lack of scientifically established guidelines and automated tool support for REST API documentation with usage examples. Existing local API documentation techniques and tools are not readily usable for the documentation of REST APIs because REST APIs have HTTP protocol specific parameters, and API clients are agonistic to the programming languages used to implement the APIs. Existing REST API documentation techniques rely on custom API definition languages that require manual effort to generate and maintain REST API documentation as a separate artifact as the API evolves.

In this reasearch, I proposed and evaluated a novel technique to solve REST API documentaiton requirements. I identified the requirements by studying the existing literature and the current state of REST API documentation in practice. The technique involves the interception of example REST API calls using an HTTP proxy server to auto-generate an accurate and updated REST API documentation.

Practioners can use the presented technique to automatically generate and maintain an updated documentation of REST APIs including the API structure and usage examples from their API test code. Researchers can apply the novel concept of using interception to automatically document API usage examples from test scripts to other forms of APIs.

\newpage
\phantomsection
\altchapter{\bf{Acknowledgements}}
